Dynein project log

### 2016-09-20 thesis_stuff/thesis_stuff.tex
Add minor change to thesis_stuff.tex.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    Ls & 12nm & & & &\\ \hline
    Lt &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & & & & &\\ \hline
    $\theta_{m}^{Post}$ & & & & &\\ \hline
    $\theta_{b}$ & 56 & & & &\\ \hline
    $\theta_{t}$ & 0 & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $1000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}

@@

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\end{itemize}
\end{document}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & &\\ \hline
    $L_t$ &  & & & &\\ \hline
    $R_b$ &  & & & &\\ \hline
    $R_m$ &  & & & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & & & & &\\ \hline
    $\theta_{m}^{Post}$ & & & & &\\ \hline
    $\theta_{b}$ & 56 & & & &\\ \hline
    $\theta_{t}$ & 0 & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$? review & & & &\\ \hline
    $k_b$ & $1000 s^{-1,b}$? review & & & &\\ \hline
  \end{tabular}
\end{center}

@@

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\end{itemize}
\end{document}
